---
title: "Create test data"
output: html
---

## Managing raster data in R

```{r install, eval=FALSE}
# install dev version of FedData for latest functionality
remotes::install_github("ropensci/FedData")

# if install_github fails, clone and install from local clone
```

```{r setup}
library(nybem)
library(dplyr)
library(FedData)
library(raster)
library(rgdal)
library(sp)
library(tmap)
library(grDevices)
library(usethis)
```

```{r set-project-crs}
# Set study area coordinate system for NJ-NY
# EPSG:6347 - NAD83(2011) / UTM zone 18N
study_area_crs <- sp::CRS(SRS_string = "EPSG:6347")
```

```{r create-palettes}
# Create a topo color ramp
esri_topo <- grDevices::colorRampPalette(colors = c("cadetblue2", "khaki1",
                                                    "chartreuse4", "goldenrod1",
                                                    "orangered4", "saddlebrown",
                                                    "gray70", "white"),
                                         bias = 1,
                                         space = "Lab",
                                         interpolate = "linear")
# Get NLCD color map palette
nlcd_pal <- FedData::pal_nlcd()
```

## Create a small test area
Create a small test study area for efficient process testing. Test are centered on the Chestnut Neck Boatyard, Garden State Parkway S, Exit 48 at Route 9, located on the Mullica River. 
```{r create-study-area}
# extent expressed in NAD83(2011) / UTM zone 18N
study_area_extent <- raster::extent(544900,547600,4376700,4379300)
study_area <- FedData::polygon_from_extent(study_area_extent, 
                                  proj4string = proj4string(study_area_crs))
```

```{r get-ned}
NED <- FedData::get_ned(template = study_area, 
                        label = 'study_area')
```

```{r get-nlcd}
NLCD <- FedData::get_nlcd(template = study_area, 
                          year = 2011, 
                          dataset = "landcover", 
                          label = 'study_area')
```

```{r test-reproject}
# Project all layers to study_area coordinate system
nlcd_utm18 <- projectRaster(NLCD, 
                            res = c(30, 30),
                            crs = study_area_crs,
                            method = "ngb")
# Mask to study area extent
nlcd_crop <- crop(nlcd_utm18, study_area)

# Snap to NLCD
ned <- projectRaster(NED, 
                     res = c(30, 30),
                     crs = study_area_crs,
                     to = nlcd_crop,
                     method = "bilinear")
```

```{r display-nlcd}
nlcd_classes <- sort(unique(values(nlcd_nj_shore)))
nlcd_cols <- dplyr::filter(pal_nlcd(), ID %in% nlcd_classes)

tm_shape(nlcd_crop) +
  tm_raster(style = "cat",
            labels = nlcd_cols$Class,
            palette = nlcd_cols$Color,
            title = "NLCD Land Cover") + 
tm_shape(study_area, 
         name = "Study Area") + 
  tm_borders() +
tm_legend(outside = TRUE, text.size = .5)
```

```{r display-ned}
tm_shape(ned) +
  tm_raster(style = "cont", 
            palette = esri_topo(1000), 
            title = "NED Elevation") + 
tm_shape(study_area, 
         name = "Study Area") + 
  tm_borders() +
tm_legend(outside = TRUE, text.size = .8)
```

```{r save-data, eval=FALSE}
#usethis::use_data(nlcd, ned)
```


## Create large study area
Create a large study area for practical process testing. The extents of this study area cover the whole of the NJ Atlantic shoreline (i.e., not including Delaware Bay), West: Wharton State Forest, Cape May; East: Sea Bright; North: Edison; South: Cape May. 

```{r create-study-area-nj-shore}
# extent expressed in NAD83(2011) / UTM zone 18N
nj_shore_extent <- raster::extent(500000,600000,4300000,4485000)
nj_shore <- FedData::polygon_from_extent(nj_shore_extent, 
                                  proj4string = proj4string(study_area_crs))
```

```{r get-ned-nj-shore, eval=TRUE}
NED_nj_shore <- FedData::get_ned(template = nj_shore, 
                                 label = 'nj_shore',
                                 res = "1",
                                 force.redo = TRUE)
NED_nj_shore
```

```{r get-nlcd-nj-shore, eval=TRUE}
NLCD_nj_shore <- FedData::get_nlcd(template = nj_shore, 
                                   label = 'nj-shore',
                                   year = 2011, 
                                   dataset = "landcover", 
                                   force.redo = TRUE)
NLCD_nj_shore
```

```{r reproject-nj-shore, eval=TRUE}
# Project all layers to study_area coordinate system
nlcd_nj_shore_utm18 <- projectRaster(NLCD_nj_shore, 
                                     res = c(30, 30),
                                     crs = study_area_crs,
                                     method = "ngb")
# Mask to study area extent
nlcd_nj_shore <- crop(nlcd_nj_shore_utm18, nj_shore)

# Snap to NLCD
ned_nj_shore <- projectRaster(NED_nj_shore, 
                              res = c(30, 30),
                              crs = study_area_crs,
                              to = nlcd_nj_shore,
                              method = "bilinear")
```

```{r display-nlcd-nj-shore}
nlcd_classes <- sort(unique(values(nlcd_nj_shore)))
nlcd_cols <- dplyr::filter(pal_nlcd(), ID %in% nlcd_classes)

tm_shape(nlcd_nj_shore) +
  tm_raster(style = "cat",
            labels = nlcd_cols$Class,
            palette = nlcd_cols$Color,
            title = "NLCD Land Cover") + 
tm_shape(nj_shore, 
         name = "NJ Shore") + 
  tm_borders() +
tm_legend(outside = TRUE, text.size = .5)
```

```{r display-ned}
tm_shape(ned_nj_shore) +
  tm_raster(style = "cont", 
            palette = esri_topo(1000), 
            title = "NED Elevation") + 
tm_shape(nj_shore,
         name = "NJ Shore") +
  tm_borders() +
tm_legend(outside = TRUE, text.size = .8)
```

```{r save-data-nj-shore, eval=FALSE}
#usethis::use_data(nlcd_nj_shore, ned_nj_shore)
```

