---
title: "Create Model Data"
output: html_document
---

# Introduction  
The purpose of this document is to create a package data frame to store the habitat model suitability index values for each model in the NYBEM feasibility study and their labels to streamline model execution and plotting. 

# Define Suitability Index Values for each Submodel

## Freshwater Tidal
```{r}
# Create the model
NYBEM.fresh.tid <- data.frame(
  salinity.per   = c(0, 20, 100),
  salinity.SIV   = c(1, 0, 0),
  veg.cover.per  = c(0, 57, 100),
  veg.cover.SIV  = c(0.1, 0.5, 1),
  deposition     = c(1, 2, 5),
  deposition.SIV = c(0, 1, 1)
)

# Create model labels
NYBEM.fresh.tid_labels <- data.frame(
  model = "Freshwater, Tidal",
  label = c("Salinity duration (% time > 0.5 psu)", "Vegetation Cover (%)", 
            "Relative Depth"),
  variable = c("salinity", "veg.cover", "deposition")
)
```

```{r fig.width=6, fig.height=6}
nybem::HSIplotter(NYBEM.fresh.tid, 
           xlab = NYBEM.fresh.tid_labels$label, 
           ylab = NYBEM.fresh.tid_labels$variable)
```

## Estuarine Intertidal
```{r}
# Create the model
NYBEM.est.int <- data.frame(
  erosion        = c(-50, 10, 50),
  erosion.SIV    = c(1,   1,  0),
  veg.cover.per  = c(0,   100, NA),
  veg.cover.SIV  = c(0.1, 1,   NA),
  deposition     = c(0, 1, NA),
  deposition.SIV = c(1, 0, NA),
  land.use.per   = c(0, 10, 100),
  land.use.SIV   = c(1, 1,  0),
  shoreline.m    = c(0,   100, 500),
  shoreline.SIV  = c(0.5, 1,   1)
)

# Create model labels
NYBEM.est.int_labels <- data.frame(
  model = "Estuarine, Intertidal", 
  labels = c("% Change in Velocity from Existing", "Vegetation Cover (%)",
              "Relative Depth", "Developed Area Within 100m (%)",
              "Distance to Armored Shoreline (m)"),
  variable = c("erosion", "veg.cover", 
                "deposition", "land.use",
                "shoreline")
)
```

```{r fig.width=6, fig.height=9}
nybem::HSIplotter(NYBEM.est.int, 
           xlab = NYBEM.est.int_labels$labels, 
           ylab = NYBEM.est.int_labels$variable)
```

## Estuarine Subtidal - Hard
```{r}
# Create the model
NYBEM.est.sub.hard <- data.frame(
  cultch     = c(0, 100, NA, NA, NA, NA, NA, NA),
  cultch.SIV = c(0, 1,   NA, NA, NA, NA, NA, NA),
  MAS        = c(0, 2, 4,    6,   8, 40, NA, NA),
  MAS.SIV    = c(0, 0, 0.05, 0.5, 1, 1,  NA, NA),
  AS         = c(0, 5, 10, 15, 20,  25,  30,  40),
  AS.SIV     = c(0, 0, 1,  1,  0.6, 0.25, 0.1, 0)
)

# Create model labels
NYBEM.est.sub.hard_labels <- data.frame(
  model = "Estuarine, Subtidal, Hard Bottom", 
  label = c("Hard Substrate (%)", "Minimum Annual Salinity (psu)", 
             "Annual Mean Salinity (psu)"),
  variable = c("cultch", "MAS", "AS")
)
```

```{r fig.width=6, fig.height=6}
nybem::HSIplotter(NYBEM.est.sub.hard, 
           xlab = NYBEM.est.sub.hard_labels$label, 
           ylab = NYBEM.est.sub.hard_labels$variable)
```

## Estuarine Subtidal - Soft, SAV
```{r}
# Create the model
NYBEM.est.sub.soft.sav <- data.frame(
  substrate.sav      = c(0, 70, 100, NA),
  substrate.sav.SIV  = c(1, 1,  0.1, NA),
  light.PLA          = c(0, 10, 22, 100),
  light.SIV          = c(0, 0,  1,  1),
  vessel.density     = c(0, 1000, 10000, NA),
  vessel.density.SIV = c(1, 1,    0.1,   NA)
)

# Create model labels
NYBEM.est.sub.soft.sav_labels <- data.frame(
  model = "Estuarine, Subtidal, Soft Bottom, Submersed Aquatic Vegetation", 
  label = c("Fine Substrate Composition (%)", "Light Available (%)",
            "Vessel Usage (tracks/year)"),
  variable = c("substrate.sav", "light.PLA", 
               "vessel.density")
)
```

```{r fig.width=6, fig.height=6}

nybem::HSIplotter(NYBEM.est.sub.soft.sav, 
           xlab = NYBEM.est.sub.soft.sav_labels$label, 
           ylab = NYBEM.est.sub.soft.sav_labels$variable)
```

## Estuarine Subtidal - Soft, Clam
```{r}
# Create the model
NYBEM.est.sub.soft.clam <- data.frame(
  salinity.clam        = c(0, 12, 12.5, 20, 25, 35, 45),
  salinity.clam.SIV    = c(0, 0, 0.25, 0.75, 1, 1, 0),
  substrate.clam.fines = c(0, 50, 90, 100, NA, NA, NA),
  substrate.clam.SIV   = c(1, 0.75, 0.25, 0,  NA, NA, NA),
  Isav                 = c(0, 0.2, 0.8, 1, NA, NA, NA),
  Isav.SIV             = c(1, 1, 0, 0, NA, NA, NA)
)

# Create model labels
NYBEM.est.sub.soft.clam_labels <- data.frame(
  model = "Estuarine, Subtidal, Soft Bottom, Hard Clam", 
  label = c("Salinity (psu)", "Fine Sediment (%)", 
            "SAV Index"),
  variable = c("salinity.clam", "substrate.clam.fines", 
               "Isav")
)
```

```{r fig.width=6, fig.height=6}
nybem::HSIplotter(NYBEM.est.sub.soft.clam, 
           xlab = NYBEM.est.sub.soft.clam_labels$label, 
           ylab = NYBEM.est.sub.soft.clam_labels$variable)
```

## Marine Intertidal
```{r}
# Create the model
NYBEM.mar.int <- data.frame(
  beach.slope.per = c(0, 10, 30, NA),
  beach.slope.SIV = c(1, 1, 0, NA),
  trel            = c(0, 0.25, 0.75, 1.0),
  exp.dur.SIV     = c(0, 1, 1, 0),
  land.use.per    = c(0, 10, 100, NA),
  land.use.SIV    = c(1, 1,  0, NA),
  shoreline.m     = c(0, 100, 500, NA),
  shoreline.SIV   = c(0, 1, 1, NA)
)

# Create model labels
NYBEM.mar.int_labels <- data.frame(
  model = "Marine, Intertidal", 
  label = c("Intertidal Zone Slope (%)", "Relative exposure duration (trel)", 
            "Developed Area Within 100m (%)", 
            "Distance to Armored Shoreline (m)"),
  variable = c("beach.slope", "exp.dur",
               "land.use", "shoreline")
)
```

```{r fig.width=6, fig.height=6}
nybem::HSIplotter(NYBEM.mar.int, 
           xlab = NYBEM.mar.int_labels$label, 
           ylab = NYBEM.mar.int_labels$variable)
```

## Marine Subtidal
```{r}
# Create the model
NYBEM.mar.sub <- data.frame(
  velocity           = c(0, 25, 50, 100),
  velocity.SIV       = c(0.6, 1, 1, 0),
  substrate.fines    = c(0, 100, NA, NA),
  substrate.SIV      = c(1, 0.1, NA, NA),
  light.PLW          = c(0, 10, 22, 100),
  light.SIV          = c(0, 0, 1, 1),
  vessel.density     = c(0, 1000, 10000, NA),
  vessel.density.SIV = c(1, 1, 0.1, NA)
)

# Create model labels
NYBEM.mar.sub_labels <- data.frame(
  model = "Marine, Subtidal",
  label = c("Velocity (m)", "Fine Substrate Composition (% fines)", 
            "Percent of Light Available (%)", "Vessel Usage (tracks/year)"),
  variable = c("velocity", "substrate.fines",
               "light", "vessel.density")
)
```

```{r fig.width=6, fig.height=6}
nybem::HSIplotter(NYBEM.mar.sub, 
           xlab = NYBEM.mar.sub_labels$label, 
           ylab = NYBEM.mar.sub_labels$variable)
```

## Marine Deep
```{r}
# Create the model
NYBEM.mar.deep <- data.frame(
  salinity.low.dur    = c(0, 50, 100, NA),
  salinity.low.SIV    = c(1, 0, 0, NA),
  velocity.low.change = c(-100, -10, 10, 100),
  velocity.low.SIV    = c(0, 1, 1, 0.8),
  light.PLW           = c(0, 10, 22, 100),
  light.SIV           = c(0, 0, 1, 1),
  vessel.density      = c(0, 1000, 10000, NA),
  vessel.density.SIV  = c(1, 1, 0.1, NA)
)

# Create model labels
NYBEM.mar.deep_labels <- data.frame(
  model = "Marine, Deepwater", 
  label = c("% Time Salinity < 30 psu", "Change in Low Velocity (%)", 
            "Light Penetration (% Reaching Bottom)", "Vessel Usage (tracks/year)"),
  variable = c("salinity.low.dur", "velocity.low.change", 
               "substrate.fines", "vessel.density")
)
```

```{r fig.width=6, fig.height=6}
nybem::HSIplotter(NYBEM.mar.deep, 
           xlab = NYBEM.mar.deep_labels$label, 
           ylab = NYBEM.mar.deep_labels$variable)
```

# Combine Submodels into List
```{r}
nybem_submodels <- list(
  NYBEM.fresh.tid         = NYBEM.fresh.tid,
  NYBEM.fresh.tid_labels  = NYBEM.fresh.tid_labels,
  NYBEM.est.int           = NYBEM.est.int,
  NYBEM.est.int_labels    = NYBEM.est.int_labels,
  NYBEM.est.sub.hard      = NYBEM.est.sub.hard,
  NYBEM.est.sub.hard_labels = NYBEM.est.sub.hard_labels, 
  NYBEM.est.sub.soft.sav  = NYBEM.est.sub.soft.sav,
  NYBEM.est.sub.soft.sav_labels = NYBEM.est.sub.soft.sav_labels, 
  NYBEM.est.sub.soft.clam = NYBEM.est.sub.soft.clam,
  NYBEM.est.sub.soft.clam_labels = NYBEM.est.sub.soft.clam_labels,
  NYBEM.mar.int           = NYBEM.mar.int,
  NYBEM.mar.int_labels    = NYBEM.mar.int_labels,
  NYBEM.mar.sub           = NYBEM.mar.sub, 
  NYBEM.mar.sub_labels    = NYBEM.mar.sub_labels,
  NYBEM.mar.deep          = NYBEM.mar.deep,
  NYBEM.mar.deep_labels   = NYBEM.mar.deep_labels
)
```

# Save data to package
```{r eval=FALSE}
usethis::use_data(nybem_submodels,
                  overwrite = TRUE)
```


