---
title: "Using `nybem`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using `nybem`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Getting Started
To install the `nybem` package, install from GitHub using the `remotes` package:
```{r install, eval=FALSE}
remotes::install_github(repo = "MVR-GIS/nybem")
```

## Load Required Packages
```{r}
library(nybem)
library(raster)
```

## List the NYBEM Models
The `nybem` package contains the models created for the ecological modeling section of the NTBEM feasibility study. Notice that the `nybem::nybem_submodels` list contains a pair of data frames for each submodel in the study. Each pair of dataframes is named for the submodel it represents (i.e., `NYBEM.fresh.tid` = Freshwater Tidal Zone habitat model). The first data frame contains the habitat variables and their matching suitability index values, while the second data frame (`*_labels`) contains the labels used in plotting.  
```{r}
# Load the model data
nybem_submodels <- nybem::nybem_submodels

# View the available submodels
names(nybem_submodels)
```

## View the Suitability Index data frame 
```{r}
# View the Freshwater Tidal model
# View table of habitat variables and their suitability index values 
nybem_submodels$NYBEM.fresh.tid
```

## View the Suitability Index model labels
```{r}
nybem_submodels$NYBEM.fresh.tid_labels
```

## Plot the Suitability Index Values
```{r fig.width=6, fig.height=6}
# Freshwater, Tidal
nybem::HSIplotter(nybem_submodels$NYBEM.fresh.tid,
                  xlab = nybem_submodels$NYBEM.fresh.tid_labels$label,
                  ylab = nybem_submodels$NYBEM.fresh.tid_labels$variable)
```

# Create Site Observations
```{r}
# Single numeric site observations
salinity   <- 40
veg.cover  <- 100
deposition <- 0
obs_1 <- list(salinity, veg.cover, deposition)
obs_1
```

```{r}
# Raster site observations
salinity_ras   <- raster::raster(ncol = 2, nrow = 2, vals = rep_len(40, 4))
veg.cover_ras  <- raster::raster(ncol = 2, nrow = 2, vals = rep_len(100, 4))
deposition_ras <- raster::raster(ncol = 2, nrow = 2, vals = rep_len(0, 4))

obs_2 <- list(salinity_ras, veg.cover_ras, deposition_ras)
obs_2
```

# Calculate Suitability Index Values
```{r}
# Suitability Index value for single numeric site observations
siv_fresh.tid_obs_1 <- nybem::SIcalc(SI = nybem_submodels$NYBEM.fresh.tid,
                                 input_proj = obs_1)
siv_fresh.tid_obs_1
```

```{r}
# Suitability Index value for raster site observations
siv_fresh.tid_obs_2 <- nybem::SIcalc(SI = nybem_submodels$NYBEM.fresh.tid,
                                 input_proj = obs_2)
siv_fresh.tid_obs_2
```


# Calculate Habitat Suitability Index
```{r}
# Calculate HSI for single numeric site observations
hsi_fresh.tid_obs_1 <- nybem::HSIcalc(si_list = siv_fresh.tid_obs_1)
hsi_fresh.tid_obs_1
```

```{r}
# Calculate HSI for raster site observations
hsi_fresh.tid_obs_2 <- nybem::HSIcalc(si_list = siv_fresh.tid_obs_2)
hsi_fresh.tid_obs_2
```


