---
title: "Using `nybem`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using `nybem`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Getting Started
To install the `nybem` package, install from GitHub using the `remotes` package:
```{r install, eval=FALSE}
remotes::install_github(repo = "MVR-GIS/nybem")
```

## Load Required Packages
```{r}
library(nybem)
library(raster)
```

## List the NYBEM Models
The `nybem` package contains the models created for the ecological modeling section of the NTBEM feasibility study. Notice that the `nybem::nybem_submodels` list contains a pair of data frames for each submodel in the study. Each pair of dataframes is named for the submodel it represents (i.e., `NYBEM.fresh.tid` = Freshwater Tidal Zone habitat model). The first data frame contains the habitat variables and their matching suitability index values, while the second data frame (`*_labels`) contains the labels used in plotting.  
```{r}
# Load the model data
nybem_submodels <- nybem::nybem_submodels

# View the available submodels
names(nybem_submodels)
```

## View the Suitability Index data frame 
```{r}
# View the Freshwater Tidal model
# View table of habitat variables and their suitability index values 
nybem_submodels$NYBEM.fresh.tid
```

## View the Suitability Index model labels
```{r}
nybem_submodels$NYBEM.fresh.tid_labels
```

## Plot the Suitability Index Values
```{r fig.width=6, fig.height=6}
# Freshwater, Tidal
nybem::HSIplotter(nybem_submodels$NYBEM.fresh.tid,
                  xlab = nybem_submodels$NYBEM.fresh.tid_labels$label,
                  ylab = nybem_submodels$NYBEM.fresh.tid_labels$variable)
```

```{r fig.width=6, fig.height=6}
# Estuarine, Subtidal, Soft Bottom, Submersed Aquatic Vegetation
nybem::HSIplotter(nybem_submodels$NYBEM.est.sub.soft.sav,
                  xlab = nybem_submodels$NYBEM.est.sub.soft.sav_labels$label,
                  ylab = nybem_submodels$NYBEM.est.sub.soft.sav_labels$variable)
```

